Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-07 code/rmarkdown/article.tex
article fixes applied2
Former-commit-id: be7e21cc9f6a8768cf2d4cf4d35b361c28b0201e

We successfully mapped the main spatial patterns of adaptive (if
present) and neutral variation for each of the 26 species. The outlier
detection methods detected adaptive genetic variation in four species.
Generally, two outlier detection methods gave fairly consistent results
(mean 87.26 \% loci per species \(\pm\) 4.97 SD). Of the species that
were associated with adaptive genetic variation, only a few loci were
detected as under selection (mean 1.77 \% loci per species \(\pm\) 1.77
SD). After identifying the loci under selection, we used NMDS analyses
to identify the main gradients of adaptive (if detected) and neutral
variation for each species. Generally, only a couple of continuous
dimensions were needed to sufficiently describe the adaptive genetic
variation for each species (all species \(K = 2\); Table S2). On the
other hand, a few more continuous dimensions were often needed for
neutral genetic variation for each species (minimum \(K = 2\); mean
\(K = 2.4230769\); max \(K = 4\); Table S2). The ordinations resulting
from the NMDS analyses were used to construct an adaptive (if present)
and neutral genetic space for each species. The spatial distribution of
these genetic spaces (Figures S29--S54) generally show patterns of
spatial autocorrelation--especially the adaptive genetic spaces (eg.
\emph{Phyteuma hemisphaericum}; S49). Additionally, most species show
east-west patterns in their intra-specific genetic variation (eg.
\emph{Dryas octopetala}; S36).

The dissimilarity matrices generated using the surrogate variables
correlated with the dissimilarity matrices based on the genetic
characteristics of individuals for most species (Table 1). Specifically,
environmental variation was found to significantly correlate with
adaptive genetic variation for one species (25 \% associated with loci
under selection; \emph{P} \textless{} 0.05; mean marginal 0.02 \(R^2\)
\(\pm\) NA SD for significant models). Additionally, geographic
distances between planning units were found to significantly correlate
with neutral genetic variation among planning units for 25 species
(96.15 \% of all the species investigated; \emph{P} \textless{} 0.05;
mean marginal 0.21 \(R^2\) \(\pm\) 0.17 SD for significant models).
These results suggest that prioritizations with different environmental
characteristics tend to have individuals with different adaptive genetic
characteristics. Similarly, planning units that are further apart tend
to have individuals with different neutral genetic characteristics.
After verifying that the geographic and environmental variables
correlate with genetic variation, the next step was to determine how
effective these variables were as surrogates in the context of
conservation planning.

The environmental and geographic variables were moderately effective
surrogates for genetic variation in most species (Figure 2). The
relationship between the proportion of adaptive genetic variation
secured in a prioritization and the proportion environment variation it
also secured differed depending on the species for which the
prioritization was generated
(\(\chi^2_{3} = {4933.62} P = pvalString(2.7275469\times 10^{-11})\)).
The slope for each species were all significantly different to zero
(minimum \textit{z} = 31.66; maximum \(P = < 0.001\); Table S3). The
explanatory power of the environmental surrogates were also generally
quite high for most species (mean 0.57 \(R^2 \pm\) 0.04 SD; Figure S56),
with exception to \emph{Carex sempervirens}. The nature of these
relationships suggest that most of the adaptive variation for a given
species can be secured in a prioritization using moderately high
environmental-based targets. Similarly, the proportion of neutral
genetic variation in a prioritization was affected by the interaction
between species and the proportion of neutral variation secured in the
prioritization (\(\chi^2_{25} = 4.462023\times 10^{4}\); \(P\) =
\textless{} 0.001). The slope for each species were also significantly
different to zero (minimum \(z value = 23.3822268\); maximum \$P = 0;
Table S3). Generally, the explanatory power of geographic variables were
higher than that of environmental variables (mean 0.55 \(R^2 \pm\) 0.13
SD; Figure S57). Compared to the environmental variables, the slopes of
the relationships suggest that very high geographic-based targets are
required to generate prioritizations that secure a sufficient proportion
of neutral genetic variation for most species. Additionally, all species
were associated with prioritizations that secured a large proportion of
environmental or geographic variation (\textgreater{} 70 \%), yet
preserved only a very small proportion of the genetic variation
(\textless{} 10 \%). These results suggest while prioritizations
generated using surrogate-based targets tend to secure more genetic
variation, prioritizations generated using just these targets can result
in poor solutions.

>>>>

We successfully mapped the main spatial patterns of adaptive (if
present) and neutral variation for each of the 26 species. The outlier
detection methods detected adaptive genetic variation in four species.
Generally, two outlier detection methods gave fairly consistent results
(mean 87.26 \% loci per species \(\pm\) 4.97 SD). Of the species that
were associated with adaptive genetic variation, only a few loci were
detected as under selection (mean 1.77 \% loci per species \(\pm\) 1.77
SD). After identifying the loci under selection, we used NMDS analyses
to identify the main gradients of adaptive (if detected) and neutral
variation for each species. Generally, only a couple of continuous
dimensions were needed to sufficiently describe the adaptive genetic
variation for each species (all species \(K = 2\); Table S2). On the
other hand, a few more continuous dimensions were often needed for
neutral genetic variation for each species (minimum \(K = 2\); mean
\(K = 2.42\); max \(K = 4\); Table S2). The ordinations resulting from
the NMDS analyses were used to construct an adaptive (if present) and
neutral genetic space for each species. The spatial distribution of
these genetic spaces (Figures S29--S54) generally show patterns of
spatial autocorrelation--especially the adaptive genetic spaces
(eg.XXXX; SXX). Additionally, most species show east-west patterns in
their intra-specific genetic variation (eg. XXXX; SXXX).

The dissimilarity matrices generated using the surrogate variables
correlated with the dissimilarity matrices based on the genetic
characteristics of individuals for most species (Table 1). Specifically,
environmental variation was found to significantly correlate with
adaptive genetic variation for one species (25 \% associated with loci
under selection; \emph{P} \textless{} 0.05; mean 0.02 marginal \(R^2\)
\(\pm\) NA SD for significant models). Additionally, geographic
distances between planning units were found to significantly correlate
with neutral genetic variation among planning units for 25 species
(96.15 \% of all the species investigated; \emph{P} \textless{} 0.05;
mean 0.21 marginal \(R^2\) \(\pm\) 0.17 SD for significant models).
These results suggest that prioritizations with different environmental
characteristics tend to have individuals with different adaptive genetic
characteristics. Similarly, planning units that are further apart tend
to have individuals with different neutral genetic characteristics.
After verifying that the geographic and environmental variables
correlate with genetic variation, the next step was to determine how
effective these variables were as surrogates in the context of
conservation planning.

The environmental and geographic variables were moderately effective
surrogates for genetic variation in most species (Figure 2). The
relationship between the proportion of adaptive genetic variation
secured in a prioritization and the proportion environment variation it
also secured differed depending on the species for which the
prioritization was generated (\({\chi^2}_{3} = {4933.62} P = < 0.001\)).
The slope for each species were all significantly different to zero
(minimum \textit{z} = 40; maximum \(P = < 0.001\); Table S3). The
explanatory power of the environmental surrogates were also generally
quite high for most species (mean 0.57 \(R^2 \pm\) 0.04 SD; Figure S56),
with exception to \emph{Carex sempervirens}. The nature of these
relationships suggest that most of the adaptive variation for a given
species can be secured in a prioritization using moderately high
environmental-based targets. Similarly, the proportion of neutral
genetic variation in a prioritization was affected by the interaction
between species and the proportion of neutral variation secured in the
prioritization (\({\chi^2}_{25} = 4.462023\times 10^{4}\); \(P\) =
\textless{} 0.001). The slope for each species were also significantly
different to zero (minimum \(z value = 23.3822268\); maximum \$P = 0;
Table S3). Generally, the explanatory power of geographic variables were
higher than that of environmental variables (mean 0.55 \(R^2 \pm\) 0.13
SD; Figure S57). Compared to the environmental variables, the slopes of
the relationships suggest that very high geographic-based targets are
required to generate prioritizations that secure a sufficient proportion
of neutral genetic variation for most species. Additionally, all species
were associated with prioritizations that secured a large proportion of
environmental or geographic variation (\textgreater{} 70 \%), yet
preserved only a very small proportion of the genetic variation
(\textless{} 10 \%). These results suggest while prioritizations
generated using surrogate-based targets tend to secure more genetic
variation, prioritizations generated using just these targets can result
in poor solutions.
